MLH1 data report 

### 2017-11-09 rmd_report.rmd
moved first functions to src dir

#MLH1_data$quality <- as.numeric(MLH1_data$quality) #this needs to be run for the subsetting to work

highest_qual_df <-  subset(MLH1_data, as.numeric(MLH1_data$quality) <= 2 )

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block

df_list <- split(MLH1_data, (MLH1_data$category))

#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16, 18) ]
#7, PERC. 12 CASTF, 14 HMI f , 16 SPRET f. 18 other

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
geom_hline(aes(yintercept = med, group = gr), colour = 'red')
for (gg in 1:length(plot_list) ){
  show(plot_list[gg])
  #invisible(lapply(obj, function(x) plot(x,main="some plot")))
}
```

>>>>

#MLH1_data$quality <- as.numeric(MLH1_data$quality) #this needs to be run for the subsetting to work
highest_qual_df <-  subset(MLH1_data, as.numeric(MLH1_data$quality) <= 2 )

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16, 18) ]
#7, PERC. 12 CASTF, 14 HMI f , 16 SPRET f. 18 other

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
geom_hline(aes(yintercept = med, group = gr), colour = 'red')

for (gg in 1:length(plot_list) ){
  show(plot_list[gg])
  #invisible(lapply(obj, function(x) plot(x,main="some plot")))
}
```
